Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-24 demystify.tex
kiss of death cold email

\begin{itemize}
    \item \textbf{Send emails to the wrong prof.}. While this is not mentioned, it is the number one reason why you don't get a reply: you send email to profs. who do not / cannot advise CS PhD students (e.g., adjunct, emeritus, teaching, non-CS, etc.). See \autoref{sec:faculty-types} for details.
    \item \textbf{Not customizing the email, too generic}: a copy and paste kind of email or those that can be sent to multiple professors with very little modifications. This shows the lack of interest and will be treated as spam.  
    \item \textbf{Self-focus} You focus too much about you and your achievements but not why you are interested in the prof.'s work (\autoref{sec:contact}). Why their work is interesting and how your background fits in.
    \item \textbf{Too long}. Keep it to about 3--4 paragraphs. Seriously, less is more and too long emails are often not read and discarded.\\
    Personally I do not want to see course transcript or CV in the first email.  If we are interested, we will ask for more information.
    \item \textbf{Flowery greetings and language}. Don't use ``Dear esteemed professor'', don't ``hey there''.  Do not call the prof. by their first name in the first email (some don't care but you don't want to take the risk -- you don't know them that well yet).  Do not use Mr., Mrs., etc. To be safe, use Prof. Lastname or Dr. Lastname (\autoref{sec:address}).
    \item \textbf{Ignoring the Prof's guideline} and asking questions that are already answered on their website (most CS profs have personal websites). For example, on my website, I put very specific information on how to contact me (e.g., email subject).  Following this helps you stand out, and I will likely respond to you than others.
    \item \textbf{Fancy format}. CS (and probably many other fields) likes plain email.  Do not use colors, fonts, or fancy formats.
    \item \textbf{Mass emails}. I've seen it many times when a student mass emails all profs in a department (e.g., through CC or even BCC---we know because faculty talk to each other).  This will result in no reply or a very harsh one on how unprofessional you are.
\end{itemize}

>>>>

\begin{itemize}
    \item \textbf{Send emails to the wrong prof.}. While this is not mentioned, it is the number one reason why you don't get a reply: you send email to profs. who do not / cannot advise CS PhD students (e.g., adjunct, emeritus, teaching, non-CS, etc.). See \autoref{sec:faculty-types} for details.
    \item \textbf{Generic}. A copy and paste kind of email or those that can be sent to multiple ppl with very little modifications. This shows the lack of interest and will be treated as spam.  
    \item \textbf{Self-focus}. Focusing too much about you and your achievements but not why you are interested in the prof.'s work (\autoref{sec:contact}). Mention why you're interested in their work and how your background can contribute. 
    \item \textbf{Too long}. Keep it to about 3--4 short paragraphs. Less is more and too long emails are often not read and discarded.\\
    Personally I do not want to see course transcript or test scores in the first email. If I am interested I'll ask for them. Attaching CV is OK. Sample papers and links to your Arxiv papers or GitHub projects are also OK if they are relevant to my work.  
    \item \textbf{Flowery greetings and language}. Don't use ``Dear esteemed professor'', don't ``hey there''.  Do not call the prof. by their first name in the first email (some don't care but you don't want to take the risk -- you don't know them that well yet).  Do not use Mr., Mrs., etc. To be safe, use Prof. Lastname or Dr. Lastname (\autoref{sec:address}).
    \item \textbf{Ignoring the Prof's guideline} and asking questions that are already answered on their website.  Most CS profs have websites and many put very specific information on how to contact them (e.g., email subject, what to include).  Following this helps you stand out and increase your chance of getting a reply.
    \item \textbf{Fancy format}. CS (and probably many other fields) prefers plain email.  Do not use colors, fonts, or fancy formats.
    \item \textbf{Mass emails}. I've seen it many times when a student mass emails all profs in a department (e.g., through CC or even BCC---we know because faculty talk to each other).  This will result in no reply or a very harsh one on how unprofessional you are.
\end{itemize}
